Viability of FTIR on fossil pollen

### 2020-12-07 manuscript.Rmd
pollen count tables; fixed authors; fixed utf formatting in references; added information from biology letters guidelines to manuscript.

---
title: 'Viability of FTIR on fossil pollen'
author: 'Florian Muthreich'
date: '2020/02/04'
output:
  bookdown::pdf_document2:
    toc: false
    extra_dependencies: ["flafter"]
bibliography: references.bib
csl: biology-letters.csl
---

@@

Abstract

```{r}
if (file.exists(here("data","output","DAL_spectra.rds"))) {
  DAL = readRDS(here("data","output","DAL_spectra.rds"))
} else {
  source(here("R","read_data.R"))
  read_data("DAL")
  DAL = readRDS(here("data","output","DAL_spectra.rds"))
}

@@

```{r}
count_grains = function(core){
  counts = core %>%
    group_by(type, depth, treatment) %>%
    summarise(count=n())
  return(counts)
}
count_grains(TSK)
```

>>>>

---
title: 'Viability of FTIR on fossil pollen'
date: '2020/02/04'
output:
  bookdown::pdf_document2:
    toc: false
    extra_dependencies: ["flafter"]
bibliography: references.bib
csl: biology-letters.csl
---

@@

2500 words not including in tables title page references
2 figs and 2 tables
figures separate legends in text
separate cover letter

# Chemistry of fossil Pinus pollen and the effect of acetolysis

## Abstract
200 words no abreviations/refs

Keywords: FTIR, fossil pollen, Holocene, density separation, acetolysis, pollen chemistry

<!-- READ DATA -->
```{r}
if (file.exists(here("data","output","DAL_spectra.rds"))) {
  DAL = readRDS(here("data","output","DAL_spectra.rds"))
} else {
  source(here("R","read_data.R"))
  read_data("DAL")
  DAL = readRDS(here("data","output","DAL_spectra.rds"))
}

@@

```{r DALcounts, echo=FALSE, results='asis'}
count_grains = function(core){
  counts = core %>%
    subset(type == "pollen" & species == "Pinus") %>% 
    group_by(type, depth, treatment) %>%
    summarise(count=n())
  return(counts)
}
kable(count_grains(DAL), booktabs = T, format = "latex",
      caption = "Pinus pollen grain count in Dalmutladdo core.")
#      digits = 1, format.args = list(scientific = F),
#      col.names = c("")) %>% 
#  add_header_above()
```

```{r TSKcounts, echo=FALSE, results='asis'}
kable(count_grains(TSK), booktabs = T, format = "latex",
      caption = "Pinus pollen grain count in Tiefer See core.")
```

```{r MFMcounts, echo=FALSE, results='asis'}
kable(count_grains(MFM), booktabs = T, format = "latex",
      caption = "Pinus pollen grain count in Meerfelder Maar core.")
```
